### 2021-05-19 LaTeX-ACM/sections/paper.tex
arb new data + small tweaks on text

\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract called the \href{https://kovan.etherscan.io/address/0xe681857defe8b454244e701ba63efaa078d7ea85}{Arbitrum EthBridge}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum. These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). \textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing.} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

@@

@@

 \subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.

>>>>

\textit{Testing Platforms.} Arbitrum currently operates a test network with a bridge contract on the Ethereum Kovan testnet. To experiment with Arbitrum, we implemented a variant of \cm and run the same experiments that we previously performed on Layer 1 (Ethereum). To call functions on \cm, traders can (i) send transactions directly to the inbox contract \href{https://kovan.etherscan.io/address/0x76bF1345224fE606E2aB38B8E52B83512328A9DF}, or (ii) use a relay server (called an \textit{Aggregator}) provided by the Arbitrum. These aggregators will group and send all pending transactions together as a single Kovan transaction to the EthBridge contract (and pay the gas).

@@

In our \cm variant on Arbitrum, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). \textblue{On Arbitrum, heaps are XX\% more efficient than non-Heaps for submitting orders and YY\% less efficient for closing (find the \% from the data provided below )} Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With Arbitrum roll-ups, 38 pairs costs only 1,544 in L1 gas (a 99.9\% savings). This is effectively the cost of recording the \texttt{closeMarket()} function call in the inbox, which is 103 bytes of calldata. As the number of pairs increases, L1 gas cost is constant. For traders submitting an order, the cost is reduced from  207,932 to 2,005.

 % Arbitrum V5 test results:

 % Heap Dynamic Array: worst case matching, 48 pairs of orders: tx hash: 0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01, L1 gas: 1632, L2 arbgas: 1,039,351
 % (https://explorer5.arbitrum.io/#/tx/0x2c0f5b5ba3539eb72018c08856c156c8098edcfd35db80f929a13c0aa6f9cc01)

@@

\textblue{Say something about sequencer.}

@@

 \subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer5.arbitrum.io/#/address/0xce17be19aa80396ae1a1c9f8dd386c48c1533f52}{[explorer5.offchainlabs.com]}.
